Belowground sink limitation alters growth and carbon balance of *Eucalyptus* seedlings

### 2016-01-06 manuscript/manuscript_pve.Rmd
caption fix
manuscript publishers additions to pve

\
Courtney E. Campany^1^, Belinda Medlyn^1^, Remko A. Duursma^1^.

\
^1^ Hawkesbury Institute for the Environment, University of Western Sydney, Locked Bag 1797, Penrith, NSW, Australia

\
*Corresponding author*:
Courtney Campany
E: courtneycampany@gmail.com

@@

pvetab1 <- "1"
pvetab2 <- "2"
pvetab3 <- "3"
pvetabS <- "S3"

@@

>>>>

\
COURTNEY E. CAMPANY^1,2^, BELINDA MEDLYN^1^ and REMKO A. DUURSMA^1^

\
^1^ Hawkesbury Institute for the Environment, University of Western Sydney, Locked Bag 1797, Penrith, NSW, Australia
\
^2^ Corresponding author (courtneycampany@gmail.com)

\
Hawkesbury Institute for the Environment, Western Sydney University
Hawkesbury Campus
Ground Floor, Building R2
Locked Bag 1797
Penrith 2751 NSW Australia

\
RUNNING HEAD:

@@

pvetab1 <- "1"
pvetab2 <- "2"
pvetab3 <- "3"
pvetabS <- "S1"

@@

# Acknowledgements
We thank Burhan Amiji for for his outstanding technical assitance. We would like to thank the many Hawkesbury Institute for the Environment staff and students who provded field work help during the experimental harvest.
